Paper 4: quasi-experiment

### 2024-10-08 Rmd/Paper4.Rmd
Added some comments and section headings

@@

@@

diff_TPACK_v23 <- post_scores_v23["TPACK","mean"] - pre_scores_v23["TPACK","mean"]
diff_p_TPACK_v23 <- wilcox.test(scores_v23_post$scores[,"TPACK"], scores_v23_pre$scores[,"TPACK"], paired=T)$p.value

# create table
rad_TK_v22 <- list("TK",
  pre_scores_v22["TK","mean"],
            pre_scores_v22["TK","sd"],
            post_scores_v22["TK","mean"],
            post_scores_v22["TK","sd"],
            paste0(format(diff_TK_v22$diff,digit=2),
                   " (p = ", 
                   format(diff_TK_v22$p.value, digits=2), 
                   ")"))

@@

rownames(prepost_table_v22) <- NULL # remove row names
rownames(prepost_table_v23) <- NULL # remove row names

pander(prepost_table_v22)
pander(prepost_table_v23)
```

>>>>

The file tpack-pilot_2022.Rdata was created by the Paper1.Rmd-script.

The file tpack-emne2_2023.Rdata was created by the datareduksjon-TPACK-PST-2023.Rmd-script, which is not published, but available by request. It is similar to the 2022-script.

@@

### Recalculate values

@@

diff_TPACK_v23 <- post_scores_v23["TPACK","mean"] - pre_scores_v23["TPACK","mean"]
diff_p_TPACK_v23 <- wilcox.test(scores_v23_post$scores[,"TPACK"], scores_v23_pre$scores[,"TPACK"], paired=T)$p.value
```

### Create table

```{r}
# create table
rad_TK_v22 <- list("TK",
  pre_scores_v22["TK","mean"],
            pre_scores_v22["TK","sd"],
            post_scores_v22["TK","mean"],
            post_scores_v22["TK","sd"],
            paste0(format(diff_TK_v22$diff,digit=2),
                   " (p = ", 
                   format(diff_TK_v22$p.value, digits=2), 
                   ")"))

@@

rownames(prepost_table_v22) <- NULL # remove row names
rownames(prepost_table_v23) <- NULL # remove row names
```

### Present results in table

This is the table that was presented in paper 4

```{r}
pander(prepost_table_v22)
pander(prepost_table_v23)
```
